### 2021-04-30 Demographics Review R markdown.Rmd
Updates

# Set working directory
setwd("~/Demographics Review")

# Download scoring sheet 
data.original <- read_excel("scoring_rhiannon.xlsx")
```

@@

  A recent study reviewed the reporting and analysis of sex in the biological sciences research [@RN1]. The authors found that while sex inclusion has significantly increased over the past 10 years, sex-based analysis has not improved, despite recent policies.

>>>>

# Set working directory
#setwd("~/Demographics Review")
setwd("~/Projects/sleep_circadian_demographics_data")

# Download scoring sheet 
data.original <- read_excel("scoring.xlsx")
```

@@

  A recent study reviewed the reporting and analysis of sex in the biological sciences research [@woitowich_a_2020, @mallampalli_exploring_2014]. The authors found that while sex inclusion has significantly increased over the past 10 years, sex-based analysis has not improved, despite recent policies.
